---
title: "r markdown output"
description: | 
  beautify html output 
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: cerulean
    number_sections: true
    highlight: tango
    df_print: paged
---
<!-- Ctrl+Shift+c: 快速注释 -->

```{r setup, include = FALSE}
library(ggplot2)
library(dplyr)

smaller <- diamonds %>% 
  filter(carat <= 2.5)
```

# theme: cerulean, flatly, journal {.tabset .tabset-fade .tabset-pills}
.tabset-fade: switching between tabs
.tabset-pills: switching between tabs and looks like pill

## toc:1-6, toc_float: keep the table of contents
output:
  html_document:
    toc: true
    toc_depth: 4
    toc_float: true
    theme: cerulean

## number_sections: true
add 1,2,3 to table of contents

## install.packages("distill")
distill::distill_article

# paged table
df_print: paged

# Using css {#css .css} or blocks 
```{css}
h1 {color: blue;}
h2 {color: green;}
```


# r code

## Using `r ` can output from r funciton

We have data about `r nrow(diamonds)` diamonds. Only
`r nrow(diamonds) - nrow(smaller)` are larger than
2.5 carats. The distribution of the remainder is shown
below:

## paged
```{r}
head(diamonds, 20)
```


## plot, echo=FALSE and the code will not show 
```{r, echo = FALSE}
smaller %>% 
  ggplot(aes(carat)) + 
  geom_freqpoly(binwidth = 0.01)
```

